Software Citation Principles

### 2016-04-18 sc-principles/software-citation-principles.tex
updating text citation discussion in 5 re https://github.com/force11/force11-scwg/issues/100

In terms of how citations should be expressed as text, such
as in journals or other human readable material, there are currently at least four styles (AMS, APA, Chicago, MLA). These have been illustrated with examples by Lipson~\cite{lipson2011cite}.
This is another area that is in flux at this time.

>>>>

Citations in the scholarly literature are formatted according to the citation style (e.g., AMS, APA, Chicago, MLA) used by that publication. (Examples illustrating these styles have been published by Lipson~\cite{lipson2011cite}.)  As these citations are typically sent to publishers as text formatted in that citation style, not as structured metadata, and because the citation style dictates how the human reader sees the software citation, \textit{we recommend that all text citation styles support the following: 
a) a label indicating that this is software, e.g.\ [Computer program], and b) support for version information, e.g.\ Version 1.8.7.}
